---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# epiverse

epiverse makes it easy to install and load the collection of R packages
maintained by the [Economic Policy Institute](https://www.epi.org/). A single
call to `library(epiverse)` attaches all included packages and reports any
function conflicts.

## Installation

``` r
install.packages(
  "epiverse",
  repos = c("https://economic.r-universe.dev", getOption("repos"))
)
```

Or from GitHub:

``` r
remotes::install_github("economic/epiverse")
```

## Usage

```{r}
library(epiverse)
```

## Packages

| Package | Description |
|---|---|
| [epidatatools](https://economic.github.io/epidatatools/) | Tools for working with EPI data |
| [epiextractr](https://economic.github.io/epiextractr/) | Extract and process CPS microdata |
| [epitargets](https://economic.github.io/epitargets/) | targets pipeline helpers for EPI projects |
| [prefab](https://economic.github.io/prefab/) | Opinionated theme system for R project scaffolding |
| [realtalk](https://economic.github.io/realtalk/) | Inflation adjustment for price data |
| [swadlr](https://economic.github.io/swadlr/) | State of Working America Data Library in R |

## Acknowledgments

This package draws heavily on the architecture of the
[tidyverse](https://tidyverse.tidyverse.org/) package by Hadley Wickham.

## License

MIT
